Plotting

### 2019-04-01 studysite_plot.Rmd
updated

```{r}
library(tidyverse)
library(viridis)
library(plyr)
library(zoo)
library(lubridate)
library(maptools)
library(sp)
library(geosphere)
library(marmap)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(mapproj)
library(fossil)
```

>>>>

```{r}
library(tidyverse)
library(viridis)
library(plyr)
library(zoo)
library(lubridate)
library(maptools)
library(sp)
library(geosphere)
library(marmap)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(mapproj)
library(fossil)

source("functions/earthdist.R") # lies in the folder labeled funtions
source("functions/scale.bar.func.R")
source("functions/shoreNormalTransectFunc.R")
```
